---
title: "Assignment 7"
author: "Landon Wilson"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)  
library(viridis)     
library(latex2exp)   
library(plotly)
library(RColorBrewer)
```

```{r include=FALSE}
data("trees")
```


### Exercise 2 {-}

Using the `datasets::trees` data, complete the following. This question refreshes create a linear model, graphing the linear model, and introduces using some LaTeX expressions on the graph.

**a)** Create a regression model for $y=$ `Volume` as a function of $x=$ `Height`.

```{r}
trees.model <- lm(trees$Volume ~ trees$Height)
```

**b)** Display the `summary` of the  model to view the y-intercept and slope of the regression line.

```{r}
summary(trees.model)
```

**c)** Using `ggplot2`, create a scatter plot of Volume vs Height. 

```{r}
ggplot(data = trees,aes(x = Height, y = Volume))+
  geom_point()
```

**d)** Color the scatter using the `Girth` variable.

```{r}
ggplot(data = trees,aes(x = Height, y = Volume))+
  geom_point(aes(color = Girth))
```

**e)** Modify the color scheme using a RColorBrewer palette.

```{r}
ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')
```

**f)** Create a nice white filled rectangle to add text information. The following might be useful.

```{r, eval=FALSE}
 annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
```

```{r}
ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')
```


**g)** Use the `broom` package to extract the coefficients of the best-fit line. Add this information as an annotation to the graph, which should follow a form that looks like $\hat{y}_i = (INTERCEPT) + (SLOPE)* x_i$. Place the annotation within the white text box.

```{r}
coef <- broom::tidy(trees.model)
int <- round(coef[1,2],3)
slope <- round(coef[2,2],3)

ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
  annotate("text", x = 70, y = 67,
           label = paste("y = ", int, " + ", slope, "x"), parse = FALSE)
```

**h)** Use the `broom` package to extract the coefficient of determination $r^2$ from the model. Add the annotation to your graph, which should look something like $R^2 = (VALUE)$

```{r}
r.2 <- round(broom::glance(trees.model)$r.squared,3)

ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
  annotate("text", x = 70, y = 70,
           label = paste("y = ", int, " + ", slope, "x"), parse = FALSE)+
  annotate("text", x = 70, y = 63,
           label = paste("R^2 = ", r.2), parse = FALSE)
```

**i)** Add the regression line in red. There are several ways to do this.

```{r}
SLM.Int <- trees.model$coefficients[1]
SLM.Slope <- trees.model$coefficients[2]

ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
  annotate("text", x = 70, y = 70,
           label = paste("y = ", int, " + ", slope, "x"), parse = FALSE)+
  annotate("text", x = 70, y = 63,
           label = paste("R^2 = ", r.2), parse = FALSE)+
  geom_abline(intercept = SLM.Int, slope = SLM.Slope, color = "red")
```

**j)** Properly label the axes of the graph.

```{r}
ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
  annotate("text", x = 70, y = 70,
           label = paste("y = ", int, " + ", slope, "x"), parse = FALSE)+
  annotate("text", x = 70, y = 63,
           label = paste("R^2 = ", r.2), parse = FALSE)+
  geom_abline(intercept = SLM.Int, slope = SLM.Slope, color = "red")+
  labs(x = "Height (ft)",
       y = "Volume (cubic ft)",
       color = "Girth (in)")
```

**k)** Add a descriptive title to the graph.

```{r}
ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point(aes(color = Girth)) +
  scale_color_viridis_c(option='magma')+
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black')+
  annotate("text", x = 70, y = 70,
           label = paste0("y = ", int, " + ", slope, "x"), parse = FALSE)+
  annotate("text", x = 70, y = 63,
           label = paste0("R^2 = ", r.2), parse = FALSE)+
  geom_abline(intercept = SLM.Int, slope = SLM.Slope, color = "red")+
  labs(title = "Tree Volume vs Height",
       x = "Height (ft)",
       y = "Volume (cubic ft)",
       color = "Girth (in)")
```


=
